---
title: "MIT Data"
output:
  pdf_document: default
  html_document: default
---

```{r pressure, echo=FALSE}
library(tidyverse)
library(rstatix)
library(ggpubr)
library(ggplot2)
library(dplyr)
library(reshape2)
library(tidyr)
library(haven)
library(fastDummies)
require(foreign)
library(plyr)
require(nnet)
library(fastDummies)
library(boot)
library(lavaan)
theme_set(theme_pubr())
```

# Load data
```{r}
virbeh <- read.csv("/Users/leilaorszag/Desktop/cleaned_data.csv")
count = data.frame(count(virbeh$school))
count$drop = count$freq <5
count[order(count$drop), ]
drop_vec = filter(count, count$drop == TRUE)
dat_sch_drop <- virbeh[!virbeh$school %in% drop_vec$x, ]
```


#cleaning by missing entries (school, pre, take a knee)
```{r}
working_data = dat_sch_drop[!(is.na(dat_sch_drop$school) | dat_sch_drop$school==""), ]
working_data = working_data[!(is.na(dat_sch_drop$cc_choice) | dat_sch_drop$cc_choice==""), ]
```


# ROC library
```{r}
library(pROC)
```


```{r}
colnames(working_data)
```

```{r}
working_data$preveducation = as.numeric(working_data$preveducation)
working_data$prevCC = gsub("No. I have never completed CrashCourse.", 1, working_data$prevCC)
working_data$prevCC = gsub("Maybe. I am unsure whether I have completed CrashCourse previously.", 2, working_data$prevCC)
working_data$prevCC = gsub("Yes. I have completed CrashCourse previously.", 3, working_data$prevCC)
working_data$matrix_pre_1 = gsub("Extremely Disagree", 1, working_data$matrix_pre_1)
working_data$matrix_pre_1 = gsub("Somewhat Disagree", 2, working_data$matrix_pre_1)
working_data$matrix_pre_1 = gsub("Somewhat Agree", 3, working_data$matrix_pre_1)
working_data$matrix_pre_1 = gsub("Extremely Agree", 4, working_data$matrix_pre_1)
working_data$matrix_pre_2 = gsub("Extremely Disagree", 1, working_data$matrix_pre_2)
working_data$matrix_pre_2 = gsub("Somewhat Disagree", 2, working_data$matrix_pre_2)
working_data$matrix_pre_2 = gsub("Somewhat Agree", 3, working_data$matrix_pre_2)
working_data$matrix_pre_2 = gsub("Extremely Agree", 4, working_data$matrix_pre_2)
```
matrix pre 3-6
```{r}
working_data$matrix_pre_3 = gsub("Extremely Disagree", 1, working_data$matrix_pre_3)
working_data$matrix_pre_3 = gsub("Somewhat Disagree", 2, working_data$matrix_pre_3)
working_data$matrix_pre_3 = gsub("Somewhat Agree", 3, working_data$matrix_pre_3)
working_data$matrix_pre_3 = gsub("Extremely Agree", 4, working_data$matrix_pre_3)
working_data$matrix_pre_4 = gsub("Extremely Disagree", 1, working_data$matrix_pre_4)
working_data$matrix_pre_4 = gsub("Somewhat Disagree", 2, working_data$matrix_pre_4)
working_data$matrix_pre_4 = gsub("Somewhat Agree", 3, working_data$matrix_pre_4)
working_data$matrix_pre_4 = gsub("Extremely Agree", 4, working_data$matrix_pre_4)
working_data$matrix_pre_5 = gsub("Extremely Disagree", 1, working_data$matrix_pre_5)
working_data$matrix_pre_5 = gsub("Somewhat Disagree", 2, working_data$matrix_pre_5)
working_data$matrix_pre_5 = gsub("Somewhat Agree", 3, working_data$matrix_pre_5)
working_data$matrix_pre_5 = gsub("Extremely Agree", 4, working_data$matrix_pre_5)
working_data$matrix_pre_6 = gsub("Extremely Disagree", 1, working_data$matrix_pre_6)
working_data$matrix_pre_6 = gsub("Somewhat Disagree", 2, working_data$matrix_pre_6)
working_data$matrix_pre_6 = gsub("Somewhat Agree", 3, working_data$matrix_pre_6)
working_data$matrix_pre_6 = gsub("Extremely Agree", 4, working_data$matrix_pre_6)
```


```{r}
working_data$cc_choice = gsub("Stay In The Game.*", 0, working_data$cc_choice)
working_data$cc_choice = gsub("Take a Knee.*", 1, working_data$cc_choice)
table(working_data$cc_choice)
run_data = data.frame(filter(working_data, working_data$cc_choice == 0 |working_data$cc_choice == 1))
table(run_data$cc_choice)
```

```{r}
run_data$matrix_pre_1 = as.numeric(run_data$matrix_pre_1)
run_data$matrix_pre_2 = as.numeric(run_data$matrix_pre_2)
run_data$matrix_pre_3 = as.numeric(run_data$matrix_pre_3)
run_data$matrix_pre_4 = as.numeric(run_data$matrix_pre_4)
run_data$matrix_pre_5 = as.numeric(run_data$matrix_pre_5)
run_data$matrix_pre_6 = as.numeric(run_data$matrix_pre_6)
run_data$prevCC= as.numeric(run_data$prevCC)
run_data$preveducation= as.numeric(run_data$preveducation)
```

```{r}
run_data$cc_choice = as.numeric(run_data$cc_choice)
```


# ROC curves for virbeh
```{r}
status.roc.list <- roc(cc_choice ~ preveducation + prevCC + matrix_pre_1 + matrix_pre_2 + matrix_pre_3 + matrix_pre_4 + matrix_pre_5 + matrix_pre_6, data = run_data, levels = c(0, 1))
rocchoiceedu <- roc(cc_choice ~ preveducation, data=run_data)
rocchoice_prev1 <- roc(cc_choice ~ matrix_pre_1, data=run_data)
rocchoice_prev2 <- roc(cc_choice ~ matrix_pre_2, data=run_data)
rocchoice_prev3 <- roc(cc_choice ~ matrix_pre_3, data=run_data)
rocchoice_prev4 <- roc(cc_choice ~ matrix_pre_4, data=run_data)
rocchoice_prev5 <- roc(cc_choice ~ matrix_pre_5, data=run_data)
rocchoice_prev6 <- roc(cc_choice ~ matrix_pre_6, data=run_data)
```

```{r}
roc.test(rocchoiceedu, rocchoice_prev1, method=c("bootstrap"))
roc.test(rocchoiceedu, rocchoice_prev2, method=c("bootstrap"))
roc.test(rocchoiceedu, rocchoice_prev3, method=c("bootstrap"))
roc.test(rocchoiceedu, rocchoice_prev4, method=c("bootstrap"))
roc.test(rocchoiceedu, rocchoice_prev5, method=c("bootstrap"))
roc.test(rocchoiceedu, rocchoice_prev6, method=c("bootstrap"))

roc.test(rocchoice_prev1, rocchoice_prev2, method=c("bootstrap"))
roc.test(rocchoice_prev1, rocchoice_prev3, method=c("bootstrap"))
roc.test(rocchoice_prev1, rocchoice_prev4, method=c("bootstrap"))
roc.test(rocchoice_prev1, rocchoice_prev5, method=c("bootstrap"))
roc.test(rocchoice_prev1, rocchoice_prev6, method=c("bootstrap"))

```




# extract auc
```{r}
status.roc.list %>% 
  map(~tibble(AUC = .x$auc)) %>% 
  bind_rows(.id = "name") -> status.data.auc

virbehlegendlabels = c("Previous Education", "Previous CC", "Enjoyment (Previous)", "Subjective Knowledge", "Reporting Intention", "Subjective Norms", "Attitudes", "Perceived Behavioral Control")
```

```{r}
virbehlegendlabels
```




# generate labels 
```{r}
status.data.auc %>% 
  mutate(label_long=paste0(virbehlegendlabels,",  AUC = ",paste(round(AUC,2))),
         label_AUC=paste0("AUC = ",paste(round(AUC,2)))) -> status.data.labels
```


```{r}
virbehROC <- ggroc(status.roc.list, size=0.6) + 
  ggtitle("Figure 1. Predicting Virtual Behavior Based on Theory of Planned Behavior Constructs and Enjoyment") + 
  labs(color='Constructs') +
  theme_bw() + 
  scale_color_discrete(labels=status.data.labels$label_long) +
  theme(axis.line = element_line(colour = "black", size=1),
        panel.border = element_blank(), 
        panel.background = element_blank(),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        plot.title = element_text(face="bold", size=11, hjust = .95, vjust = -0.5),
        legend.title = element_text(size=10, face="bold", hjust = 0.5),
        legend.text=element_text(size=10),
        axis.title.x = element_text(face="bold", size=8),
        axis.title.y = element_text(face="bold", size=8),
        axis.text = element_text(size=9),
        legend.background = element_rect(size=0.5, linetype="solid", color ="black"),
        legend.justification=c(1,0),
        legend.position=c(0.9,0.1),
        legend.key.width=unit(0.5,"line"),
        legend.key.height=unit(0.6,"line")) 
```


```{r}
virbehROC
```

Previous Education vs CC_Choice (SIGNIFICANT)
```{r}
VirtualReport_preved <- glm(cc_choice ~ preveducation, data=run_data, family=binomial(link="logit"))
summary(VirtualReport_preved)
exp(summary(VirtualReport_preved)$coefficients["preveducation",1] +
      +     qnorm(c(0.025,0.5,0.975)) * summary(VirtualReport_preved)$coefficients["preveducation",2])
```

Previous CC vs CC_Choice (SIGNIFICANT)

```{r}
VirtualReport_prevCC <- glm(cc_choice ~ prevCC, data=run_data, family=binomial(link="logit"))
summary(VirtualReport_prevCC)
exp(summary(VirtualReport_prevCC)$coefficients["prevCC",1] +
      +     qnorm(c(0.025,0.5,0.975)) * summary(VirtualReport_prevCC)$coefficients["prevCC",2])
```


Matrix Pre 1(Previous Enjoyment) vs CC_Choice (SIGNIFICANT)
```{r}
VirtualReport_enj <- glm(cc_choice ~ matrix_pre_1, data=run_data, family=binomial(link="logit"))
summary(VirtualReport_enj)
exp(summary(VirtualReport_enj)$coefficients["matrix_pre_1",1] +
      +     qnorm(c(0.025,0.5,0.975)) * summary(VirtualReport_enj)$coefficients["matrix_pre_1",2])
```


Matrix Pre 2(Subjective Knowledge) vs CC_Choice (SIGNIFICANT)
```{r}
VirtualReport_subjknow <- glm(cc_choice ~ matrix_pre_2, data=run_data, family=binomial(link="logit"))
summary(VirtualReport_subjknow)
exp(summary(VirtualReport_subjknow)$coefficients["matrix_pre_2",1] +
      +     qnorm(c(0.025,0.5,0.975)) * summary(VirtualReport_subjknow)$coefficients["matrix_pre_2",2])
```

Matrix Pre 3(Reporting Intention) vs CC_Choice (SIGNIFICANT)
```{r}
VirtualReport_intent <- glm(cc_choice ~ matrix_pre_3, data=run_data, family=binomial(link="logit"))
summary(VirtualReport_intent)
exp(summary(VirtualReport_intent)$coefficients["matrix_pre_3",1] +
      +     qnorm(c(0.025,0.5,0.975)) * summary(VirtualReport_intent)$coefficients["matrix_pre_3",2])
```

Matrix Pre 4(Subjective Norms) vs CC_Choice (SIGNIFICANT)
```{r}
VirtualReport_norm <- glm(cc_choice ~ matrix_pre_4, data=run_data, family=binomial(link="logit"))
summary(VirtualReport_norm)
exp(summary(VirtualReport_norm)$coefficients["matrix_pre_4",1] +
      +     qnorm(c(0.025,0.5,0.975)) * summary(VirtualReport_norm)$coefficients["matrix_pre_4",2])
```


Matrix Pre 5(Attitudes) vs CC_Choice (SIGNIFICANT)
```{r}
VirtualReport_att <- glm(cc_choice ~ matrix_pre_5, data=run_data, family=binomial(link="logit"))
summary(VirtualReport_att)
exp(summary(VirtualReport_att)$coefficients["matrix_pre_5",1] +
      +     qnorm(c(0.025,0.5,0.975)) * summary(VirtualReport_att)$coefficients["matrix_pre_5",2])
```

Matrix Pre 6(Perceived Behavioral Control) vs CC_Choice (SIGNIFICANT)
```{r}
VirtualReport_control <- glm(cc_choice ~ matrix_pre_6, data=run_data, family=binomial(link="logit"))
summary(VirtualReport_control)
exp(summary(VirtualReport_control)$coefficients["matrix_pre_6",1] +
      +     qnorm(c(0.025,0.5,0.975)) * summary(VirtualReport_control)$coefficients["matrix_pre_6",2])
```

Full Significance Model

```{r}
VirtualReport_full <- glm(cc_choice ~ matrix_pre_6 + matrix_pre_5 + matrix_pre_4 + matrix_pre_3 + matrix_pre_2 + matrix_pre_1 + preveducation + prevCC, data=run_data, family=binomial(link="logit"))
summary(VirtualReport_full)
```

```{r}
Enjoy_PrevCC <- lm(matrix_pre_2 ~ prevCC, data=run_data)
summary(Enjoy_PrevCC)
confint(Enjoy_PrevCC,'prevCC')
```

```{r}
length(unique(run_data$school))
```

